Blocking-resistant communication through high-value web services

### 2014-05-13 docs/meek.tex
Spell check.

meek may be regarded as a steganographic transport only in that it must blend in with other HTTPS traffic.
Tunnelling inside HTTPS greatly eases the steganography problem:
It's not necessary to generate plausible HTTP, only plausible TLS,
because TLS payloads are encrypted, and to a first approximation all encrypted payloads look alike.
We need only make sure that the TLS handshake and other meta-attributes of the connection are not uniquely fingerprintable.
Section~\ref{sec:browserextension} describes the use of a web browser extension as a instrument for making HTTPS requests,
so things like the TLS handshake, DNS lookup, and TCP connection reuse match those of a browser as closely as possible.
Of course, there are more subtle considerations that go into
making a circumvention HTTPS stream look like an allowed HTTPS stream,
things like packet size and timing, and duration of TCP connections.
These additional considerations are the subject of Section~\ref{sec:trafficstatistics}.

@@

GoAgent~\cite{goagent} is a direct inspiration for our system in its use of App
Engine and Host header--based domain fronting.
As in our system, traffic is fronted by the Google frontend server
and delivered to its destination by a specialized app running on App Engine.
GoAgent requires users to upload a personal copy of the server code to App Engine,
which harms usability but requires no central management
and enables users to stay within bandwidth limits that exist for unpaid apps.
GoAgent is an HTTP and HTTPS proxy only.
It works by encapulating a desired HTTP request, including URL and POST body, if any,
and uploading the request to App Engine.
The app unpacks the encapsulated request and directly requests the desired URL using
App Engine's URL-fetching API.
The design is simple but has disadvantages, stemming from the web app's
need to know what URL to request.
In order to proxy HTTPS, the local GoAgent proxy program does a benign man-in-the-middle
attack on the browser, which must have previously trusted the GoAgent CA certificate.
The local proxy program decrypts the HTTPS in order to read from it the HTTP request including the URL.
When the response comes back, the local proxy re-encrypts it under its own key.
End-to-end security is lost; an attacker positioned at the web app
is able to observe and modify all traffic.
In our system, such an attacker may only deny service or perform traffic analysis on ciphertext.
Additionally, we allow proxying of any TCP-based traffic, not only HTTP.
According to a May 2013 survey~\cite{collateral-freedom},
GoAgent was the circumvention tool most used in
China, with 35\% of survey respondents having used it in the previous month.
This figure is higher than that of paid~(29\%) and free VPNs~(18\%), and far
above that of other special-purpose tools like Tor~(2.9\%) and Psiphon~(2.5\%).
Users identified reliability, speed, and ease of installation as the most important features of a circumvention tool.

@@

The censor must operate at line rate; that is,
it must not delay traffic unduly while deciding whether to allow it.
This consideration is one facet of the censor's sensistivity to
collateral damage caused by false positives:
mistakenly blocking or degrading non-circumvention traffic causes the censor
to incur some penalty, just as mistakenly allowing circumvention traffic does.
The censor must allow TLS connections; meek does not try to look like plaintext.
% but the censor may look at TLS characteristics and block suspicious connections.

@@

We implemented meek as a pluggable transport~\cite{pt} for Tor.
Although it is possible to use the system with proxies other than Tor,
using Tor has some attractive features.
The pluggable transports infrastructure makes it relatively easy to prototype
a circumvention technique and connect it to a global proxy network.
We can treat confidentiality and integrity of tunnelled communication
as a problem solved by Tor, which we don't need to solve separately.
Tor's extra proxy hops mean that the HTTP reflector (App Engine)
and the entry bridge do not have to be trusted.

@@

\section{Acknowledgements}

>>>>

meek may be regarded as a steganographic transport only in that it must blend in with other HTTPS traffic.
Tunneling inside HTTPS greatly eases the steganography problem:
It's not necessary to generate plausible HTTP, only plausible TLS,
because TLS payloads are encrypted, and to a first approximation all encrypted payloads look alike.
We need only make sure that the TLS handshake and other meta-attributes of the connection are not uniquely fingerprintable.
Section~\ref{sec:browserextension} describes the use of a web browser extension as a instrument for making HTTPS requests,
so things like the TLS handshake, DNS lookup, and TCP connection reuse match those of a browser as closely as possible.
Of course, there are more subtle considerations that go into
making a circumvention HTTPS stream look like an allowed HTTPS stream,
things like packet size and timing, and duration of TCP connections.
These additional considerations are the subject of Section~\ref{sec:trafficstatistics}.

@@

GoAgent~\cite{goagent} is a direct inspiration for our system in its use of App
Engine and Host header--based domain fronting.
As in our system, traffic is fronted by the Google frontend server
and delivered to its destination by a specialized app running on App Engine.
GoAgent requires users to upload a personal copy of the server code to App Engine,
which harms usability but requires no central management
and enables users to stay within bandwidth limits that exist for unpaid apps.
GoAgent is an HTTP and HTTPS proxy only.
It works by encapsulating a desired HTTP request, including URL and POST body, if any,
and uploading the request to App Engine.
The app unpacks the encapsulated request and directly requests the desired URL using
App Engine's URL-fetching API.
The design is simple but has disadvantages, stemming from the web app's
need to know what URL to request.
In order to proxy HTTPS, the local GoAgent proxy program does a benign man-in-the-middle
attack on the browser, which must have previously trusted the GoAgent CA certificate.
The local proxy program decrypts the HTTPS in order to read from it the HTTP request including the URL.
When the response comes back, the local proxy re-encrypts it under its own key.
End-to-end security is lost; an attacker positioned at the web app
is able to observe and modify all traffic.
In our system, such an attacker may only deny service or perform traffic analysis on ciphertext.
Additionally, we allow proxying of any TCP-based traffic, not only HTTP.
According to a May 2013 survey~\cite{collateral-freedom},
GoAgent was the circumvention tool most used in
China, with 35\% of survey respondents having used it in the previous month.
This figure is higher than that of paid~(29\%) and free VPNs~(18\%), and far
above that of other special-purpose tools like Tor~(2.9\%) and Psiphon~(2.5\%).
Users identified reliability, speed, and ease of installation as the most important features of a circumvention tool.

@@

The censor must operate at line rate; that is,
it must not delay traffic unduly while deciding whether to allow it.
This consideration is one facet of the censor's sensitivity to
collateral damage caused by false positives:
mistakenly blocking or degrading non-circumvention traffic causes the censor
to incur some penalty, just as mistakenly allowing circumvention traffic does.
The censor must allow TLS connections; meek does not try to look like plaintext.
% but the censor may look at TLS characteristics and block suspicious connections.

@@

We implemented meek as a pluggable transport~\cite{pt} for Tor.
Although it is possible to use the system with proxies other than Tor,
using Tor has some attractive features.
The pluggable transports infrastructure makes it relatively easy to prototype
a circumvention technique and connect it to a global proxy network.
We can treat confidentiality and integrity of tunneled communication
as a problem solved by Tor, which we don't need to solve separately.
Tor's extra proxy hops mean that the HTTP reflector (App Engine)
and the entry bridge do not have to be trusted.

@@

\section{Acknowledgments}
